Hypertension and microbiome

### 2019-05-06 articletwo.Rmd
Minor

pcoa.plot <- ggplot(data=pcoa.df, aes(x=Axis.1, y=Axis.2, color = STATETREATMENT, shape = STATETREATMENT)) +
    geom_point(size=0.4, alpha=0.4) +
    xlab(paste("PCoA axis 1,", round(100*eig.fracs[1],1), "%")) +
    ylab(paste("PCoA axis 2,", round(100*eig.fracs[2],1), "%")) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Hypertensive, medication",
                                   "Hypertensive, no medication",
                                   "Normotensive, no medication"),
                        breaks=c("11", "10", "00"),
                        values = c("red", "red", "blue", "blue")) +   
    scale_shape_manual(name = "State and treatment",
                       labels = c("Hypertensive, medication",
                                  "Hypertensive, no medication",
                                  "Normotensive, no medication"),
                       breaks = c("11", "10", "00"),
                       values = c(4, 1, 1))+
    coord_fixed() +
    scale_x_continuous(breaks=seq(-100, 100, 20)) +
    scale_y_continuous(breaks=seq(-30, 30, 10)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4))) +
    theme(text = element_text(size=14),
          legend.title = element_blank(),
          legend.text=element_text(size=10),
          legend.justification=c(1,0),
          legend.position=c(1,0),
          legend.margin=margin(t = 1, unit='mm'),
          legend.background = element_rect(fill=alpha('gray', 0.1)))

>>>>

pcoa.plot <- ggplot(data=pcoa.df, aes(x=Axis.1, y=Axis.2, color = STATETREATMENT, shape = STATETREATMENT)) +
    geom_point(size=0.4, alpha=0.4) +
    xlab(sprintf("PCoA Axis 1 (%.1f%%)", 100*eig.fracs[1])) +
    ylab(sprintf("PCoA Axis 2 (%.1f%%)", 100*eig.fracs[2])) +
    scale_colour_manual(name = "State and treatment",
                        labels = c("Hypertensive, medication",
                                   "Hypertensive, no medication",
                                   "Normotensive, no medication"),
                        breaks=c("11", "10", "00"),
                        values = c("red", "red", "blue", "blue")) +   
    scale_shape_manual(name = "State and treatment",
                       labels = c("Hypertensive, medication",
                                  "Hypertensive, no medication",
                                  "Normotensive, no medication"),
                       breaks = c("11", "10", "00"),
                       values = c(4, 1, 1))+
    coord_fixed() +
    scale_x_continuous(breaks=seq(-100, 100, 20)) +
    scale_y_continuous(breaks=seq(-30, 30, 10)) +
    theme_classic() +
    guides(colour = guide_legend(override.aes = list(size=4))) +
    theme(text = element_text(size=14),
          legend.title = element_blank(),
          legend.text=element_text(size=10),
          legend.justification=c(1,0),
          legend.position=c(1,0),
          legend.margin=margin(t = 1, unit='mm'),
          legend.background = element_rect(fill=alpha('gray', 0.1)))
